イーサリアム: 安全な分散型汎用トランザクション台帳\\ \smaller \textbf{{Berlin version \YellowPaperVersionNumber}}

### 2022-07-19 Paper.tex
[WIP] error: Unicode-character

We have introduced, discussed and formally defined the protocol of Ethereum. Through this protocol the reader may implement a node on the Ethereum network and join others in a decentralised secure social operating system. Contracts may be authored in order to algorithmically specify and autonomously enforce rules of interaction.

>>>>

% We have introduced, discussed and formally defined the protocol of Ethereum. Through this protocol the reader may implement a node on the Ethereum network and join others in a decentralised secure social operating system. Contracts may be authored in order to algorithmically specify and autonomously enforce rules of interaction.
我々は、イーサリアムのプロトコルを紹介し、議論し、正式に定義した。このプロトコルにより、読者はイーサリアムネットワーク上のノードを実装し、分散型の安全な社会的オペレーティングシステムに他の人と参加することができます。

契約は、相互作用のルールをアルゴリズムで指定し、自律的に強制するために作成されるかもしれません
